DOpElib:\\ Differential Equations and Optimization Environment

### 2019-04-29 Examples/OPT/StatPDE/Example10/content.tex
Fixed Typo in Docu

\textbf{\texttt{localpde.h}}
There is a new method \texttt{unsigned int NeedPrecomputations() const}
returning the value $1$ as we need one calculation of $k$ before we can
assemble the value of the cost-functional.

>>>>

\textbf{\texttt{localfunctional.h}}
There is a new method \texttt{unsigned int NeedPrecomputations() const}
returning the value $1$ as we need one calculation of $k$ before we can
assemble the value of the cost-functional.
